\huge Tor's Usability for Censorship Circumvention

### 2016-05-09 pets2017-paper/pets2017-paper.tex
Explain ``not running'' better.

\begin{figure*}
\centering
% This is a manually edited version of the automatically generated
% all-participant-edges graphic. It is edited to have better scale labels for
% the treatments.
\includegraphics{all-participant-edges-scales}
\caption{
Summary of participants' actions throughout the entire experiment.
Different colors indicate which screen was shown at each moment.
The narrow black lines show the times when the configuration interface
was not running; i.e., a participant was doing something else
such as searching the web in another browser.
The overall length of the lines show the total time to completion,
except for those we cut off after approximately 40 minutes
(marked with a $\times$).
}
\label{fig:all-participant-edges}
\end{figure*}

>>>>

\begin{figure*}
\centering
% This is a manually edited version of the automatically generated
% all-participant-edges graphic. It is edited to have better scale labels for
% the treatments.
\includegraphics{all-participant-edges-scales}
\caption{
Summary of participants' actions throughout the entire experiment.
Different colors indicate which screen was shown at each moment.
The ``not running'' times are those when Tor Launcher was closed;
i.e., a participant was doing something else
such as searching the web in another browser.
The overall length of the lines show the total time to completion,
except for those we cut off after approximately 40 minutes
(marked with a $\times$).
}
\label{fig:all-participant-edges}
\end{figure*}
